Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 revise/revise.tex
responses in revise doc to handle the concern about unmatched fidelity
moves complaint about bibliography to appropriate section

Other important works have been prepared in China in the frame of the Chinese MSR program.
\begin{solution}
        Thank you for the excellent recommendations. The new text reads thus:

@@

\question The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.

>>>>

Other important works have been prepared in China in the frame of the Chinese MSR program.

The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
\begin{solution}
        Thank you for the excellent recommendations. The new text reads thus:

@@
